Reasoning About a Machine with Local Capabilities

### 2018-05-08 toplas/paper.tex

%% Appendix
\appendix
\section{Appendix}
\subsection{Logical relation}
\label{app:logical-relation}
% Text of appendix \ldots
\textbf{$n$-subset simulation}
\begin{mathpar}
  \inferrule{(s,\phi_\pub,\phi) = (s',\phi_\pub',\phi') \\
    \forall \hat{W} \ldotp H \; s \; \hat{W} \nsubeq H' \; s' \; \hat{W} }
  { (v,s,\phi_\pub,\phi,H) \nsubsim (v',s',\phi_\pub',\phi',H')}
\end{mathpar}
\textbf{Erasure}
\begin{align*}
  \lfloor W \rfloor_S \defeq \lambda r \ldotp 
  \begin{cases}
    W(r) & W(r).v \in S\\
    \bot & \text{otherwise}
  \end{cases}
\end{align*}
\textbf{Active region projection}
\begin{align*}
  \activeReg{} & : \Worlds \fun 2^\RegionNames \\
  \activeReg{W} & \defeq \dom(\erase{W}{\perma,\temp})
\end{align*}
\textbf{Projection of regions based on locality}
\[
  \localityReg(\gl,W) \defeq 
  \begin{cases}
    \dom(\erase{W}{\perm,\temp}) & \text{if } \gl = \local \\
    \dom(\erase{W}{\perm}) & \text{if } \gl = \glob
  \end{cases}
\]
\textbf{Address stratification}
\begin{align*}
&\iota = (v,s,\phi_\pub,\phi,H) \text{ is address-stratified iff }\\
&\qquad\begin{multlined}
  \forall s', \hat{W}, n, \ms, \ms' \ldotp \\
  \npair{\ms},\npair{\ms'} \in H~ s'~ \hat{W} \Rightarrow \\
  \dom(\ms) = \dom(\ms') \wedge \\
  \forall \addr \in
  \dom(\ms)\ldotp \npair{\ms\update{\addr}{\ms'(\addr)}} \in H~ s'~ \hat{W}
\end{multlined}
\end{align*}

>>>>

%% Appendix
\appendix
\section{Appendix}
In this appendix, we give more precise formulations of lemmas that were mentioned in the paper, and the most important supporting definitions and lemmas.
The goal is to provide details that can help to understand in more detail what we discuss in the paper. 
Full details and proofs are not given here, but for those we refer to the technical appendix~\citep{technical_appendix}.

\subsection{Logical relation}
\label{app:logical-relation}
% Text of appendix \ldots
\textbf{$n$-subset simulation}
\begin{mathpar}
  \inferrule{(s,\phi_\pub,\phi) = (s',\phi_\pub',\phi') \\
    \forall \hat{W} \ldotp H \; s \; \hat{W} \nsubeq H' \; s' \; \hat{W} }
  { (v,s,\phi_\pub,\phi,H) \nsubsim (v',s',\phi_\pub',\phi',H')}
\end{mathpar}
\textbf{Erasure}
\begin{align*}
  \lfloor W \rfloor_S \defeq \lambda r \ldotp 
  \begin{cases}
    W(r) & W(r).v \in S\\
    \bot & \text{otherwise}
  \end{cases}
\end{align*}
\textbf{Active region projection}
\begin{align*}
  \activeReg{} & : \Worlds \fun 2^\RegionNames \\
  \activeReg{W} & \defeq \dom(\erase{W}{\perma,\temp})
\end{align*}
\textbf{Projection of regions based on locality}
\[
  \localityReg(\gl,W) \defeq 
  \begin{cases}
    \dom(\erase{W}{\perm,\temp}) & \text{if } \gl = \local \\
    \dom(\erase{W}{\perm}) & \text{if } \gl = \glob
  \end{cases}
\]
\textbf{Address stratification}
\begin{align*}
&\iota = (v,s,\phi_\pub,\phi,H) \text{ is address-stratified iff }\\
&\qquad\begin{multlined}
  \forall s', \hat{W}, n, \ms, \ms' \ldotp \\
  \npair{\ms},\npair{\ms'} \in H~ s'~ \hat{W} \Rightarrow \\
  \dom(\ms) = \dom(\ms') \wedge \\
  \forall \addr \in
  \dom(\ms)\ldotp \npair{\ms\update{\addr}{\ms'(\addr)}} \in H~ s'~ \hat{W}
\end{multlined}
\end{align*}
